\NewBibliographyString{alappeals,alcivilappeals,alcriminalappeals,alsupreme,akappeals,aksupreme,azappeals,azsupreme,arappeals,arsupreme,caappellatediv,caappeal,casupreme,coappeals,cosupreme,ctappellate,ctsupreme,dechancery,desuperior,desupreme,dcappeals,fldappeals,flsupreme,gaappeals,gasupreme,hiintermediateappeals,hisupreme,idappeals,idsupreme,ilappellate,ilsupreme,inappellate,inappeals,insupreme,iaappeals,iasupreme,ksappeals,kssupreme,kyappeals,kysupreme,laappeals,lasupreme,mesupremejudicial,mdspecialappeals,mdappeals,maappeals,masupremejudicial,miappeals,misupreme,mnappeals,mnsupreme,msappeals,mssupreme,moappeals,mosupreme,mtsupreme,neappeals,nesupreme,nvsupreme,nhsupreme,njappellatediv,njsupreme,nmappeals,nmsupreme,nyappellatediv,nyappellateterm,nyappeals,ncappeals,ncsupreme,ndappeals,ndsupreme,ohappeals,ohsupreme,okappeals,okcivilappeals,okcriminalappeals,oksupreme,orappeals,orsupreme,pacommonwealth,pasuperior,pasupreme,risupreme,scappeals,scsupreme,sdsupreme,tnappeals,tncriminalappeals,tnsupreme,txappeals,txcivilappeals,txcriminalappeals,txsupreme,utappeals,utsupreme,vtsupreme,vaappeals,vasupreme,waappeals,wasupreme,wvsupremeappeals,wiappeals,wisupreme,wysupreme,wyfederals,1stcir,dme,dma,dnh,dpr,dri,1stcirbankruptcy,1stcirbankruptcyappellate,2ndcir,dct,dvt,edny,ndny,sdny,wdny,2ndcirbankruptcy,2ndcirbankruptcyappellate,3rdcir,dde,dnj,dvi,edpa,mdpa,wdpa,3rdcirbankruptcy,4thcir,dmd,dsc,ednc,mdnc,wdnc,edva,wdva,ndwv,sdwv,4thcirbankruptcy,5thcir,edla,mdla,wdla,ndms,sdms,edtx,ndtx,sdtx,wdtx,5thcirbankruptcy,6thcir,edky,wdky,edmi,wdmi,ndoh,sdoh,edtn,mdtn,wdtn,6thcirbankruptcy,6thcirbankruptcyappellate,7thcir,cdil,ndil,sdil,ndin,sdin,edwi,wdwi,7thcirbankruptcy,8thcir,8thcirminnesota,dne,dnd,dsd,edar,wdar,ndia,sdia,edmo,wdmo,8thcirbankruptcy,8thcirbankruptcyappellate,9thcir,dak,daz,dgu,dhi,did,dmt,dnv,dor,cdca,edca,ndca,sdca,edwa,wdwa,9thcirbankruptcy,9thcirbankruptcyappellate,10thcir,dco,dks,dnm,dut,dwy,edok,ndok,wdok,10thcirbankruptcy,10thcirbankruptcyappellate,11thcir,mdal,ndal,sdal,mdfl,ndfl,sdfl,mdga,ndga,sdga,11thcirbankruptcy,dccir,dccirdc,dccirbankruptcy}
\DeclareBibliographyStrings{
alappeals={{Alabama Court of Appeals}{Al.  App.}},
alcivilappeals={{Alabama Court of Civil Appeals}{Al.  Civ. App.}},
alcriminalappeals={{Alabama Court of Criminal Appeals}{Al.  Crim. App.}},
alsupreme={{Alabama Supreme Court}{Al.}},
akappeals={{Alaska Court of Appeals}{Ak.  App.}},
aksupreme={{Alaska Supreme Court}{Ak.}},
azappeals={{Arizona Court of Appeals}{Az.  App.}},
azsupreme={{Arizona Supreme Court}{Az.}},
arappeals={{Arkansas Court of Appeals}{Ar.  App.}},
arsupreme={{Arkansas Supreme Court}{Ar.}},
caappellatediv={{California Appellate Div.}{Ca. Apll. Div.}},
caappeal={{California Court of Appeal}{Ca.  App.}},
casupreme={{California Supreme Court}{Ca.}},
coappeals={{Colorado Court of Appeals}{Co.  App.}},
cosupreme={{Colorado Supreme Court}{Co.}},
ctappellate={{Connecticut Appellate Court}{Ct. Apll. Court}},
ctsupreme={{Connecticut Supreme Court}{Ct.}},
dechancery={{Delaware Court of Chancery}{De.  Chancery}},
desuperior={{Delaware Superior Court}{De. Sup. Court}},
desupreme={{Delaware Supreme Court}{De.}},
dcappeals={{Dist. of Columbia Court of Appeals}{D.I.S.T...O.F.C.O.L.U.M.B.I.A.}},
fldappeals={{Florida Dist. Court of Appeals}{Fl. Dist.App.}},
flsupreme={{Florida Supreme Court}{Fl.}},
gaappeals={{Georgia Court of Appeals}{Ga.  App.}},
gasupreme={{Georgia Supreme Court}{Ga.}},
hiintermediateappeals={{Hawaii Intermediate Court of Appeals}{Hi. Int.App.}},
hisupreme={{Hawaii Supreme Court}{Hi.}},
idappeals={{Idaho Court of Appeals}{Id.  App.}},
idsupreme={{Idaho Supreme Court}{Id.}},
ilappellate={{Illinois Appellate Court}{Il. Apll. Court}},
ilsupreme={{Illinois Supreme Court}{Il.}},
inappellate={{Indiana Appellate Court}{In. Apll. Court}},
inappeals={{Indiana Court of Appeals}{In.  App.}},
insupreme={{Indiana Supreme Court}{In.}},
iaappeals={{Iowa Court of Appeals}{Ia.  App.}},
iasupreme={{Iowa Supreme Court}{Ia.}},
ksappeals={{Kansas Court of Appeals}{Ks.  App.}},
kssupreme={{Kansas Supreme Court}{Ks.}},
kyappeals={{Kentucky Court of Appeals}{Ky.  App.}},
kysupreme={{Kentucky Supreme Court}{Ky.}},
laappeals={{Louisiana Court of Appeals}{La.  App.}},
lasupreme={{Louisiana Supreme Court}{La.}},
mesupremejudicial={{Maine Supreme Judicial Court}{Me.}},
mdspecialappeals={{Maryland Court of Special Appeals}{Md.  Special App.}},
mdappeals={{Maryland Court of Appeals}{Md.}},
maappeals={{Massachusetts Appeals Court}{Ma. App. Court}},
masupremejudicial={{Massachusetts Supreme Judicial Court}{Ma.}},
miappeals={{Michigan Court of Appeals}{Mi.  App.}},
misupreme={{Michigan Supreme Court}{Mi.}},
mnappeals={{Minnesota Court of Appeals}{Mn.  App.}},
mnsupreme={{Minnesota Supreme Court}{Mn.}},
msappeals={{Mississippi Court of Appeals}{Ms.  App.}},
mssupreme={{Mississippi Supreme Court}{Ms.}},
moappeals={{Missouri Court of Appeals}{Mo.  App.}},
mosupreme={{Missouri Supreme Court}{Mo.}},
mtsupreme={{Montana Supreme Court}{Mt.}},
neappeals={{Nebraska Court of Appeals}{Ne.  App.}},
nesupreme={{Nebraska Supreme Court}{Ne.}},
nvsupreme={{Nevada Supreme Court}{Nv.}},
nhsupreme={{New Hampshire Supreme Court}{N.H.}},
njappellatediv={{New Jersey Appellate Div.}{N.J. Apll. Div.}},
njsupreme={{New Jersey Supreme Court}{N.J.}},
nmappeals={{New Mexico Court of Appeals}{N.M.  App.}},
nmsupreme={{New Mexico Supreme Court}{N.M.}},
nyappellatediv={{New York Appellate Div.}{N.Y. Apll. Div.}},
nyappellateterm={{New York Appellate Term}{N.Y. Apll. Term}},
nyappeals={{New York Court of Appeals}{N.Y.}},
ncappeals={{North Carolina Court of Appeals}{N.C.  App.}},
ncsupreme={{North Carolina Supreme Court}{N.C.}},
ndappeals={{North Dakota Court of Appeals}{N.D.  App.}},
ndsupreme={{North Dakota Supreme Court}{N.D.}},
ohappeals={{Ohio Court of Appeals}{Oh.  App.}},
ohsupreme={{Ohio Supreme Court}{Oh.}},
okappeals={{Oklahoma Court of Appeals}{Ok.  App.}},
okcivilappeals={{Oklahoma Court of Civil Appeals}{Ok.  Civ. App.}},
okcriminalappeals={{Oklahoma Court of Criminal Appeals}{Ok.  Crim. App.}},
oksupreme={{Oklahoma Supreme Court}{Ok.}},
orappeals={{Oregon Court of Appeals}{Or.  App.}},
orsupreme={{Oregon Supreme Court}{Or.}},
pacommonwealth={{Pennsylvania Commonwealth Court}{Pa. Com. Court}},
pasuperior={{Pennsylvania Superior Court}{Pa. Sup. Court}},
pasupreme={{Pennsylvania Supreme Court}{Pa.}},
risupreme={{Rhode Island Supreme Court}{R.I.}},
scappeals={{South Carolina Court of Appeals}{S.C.  App.}},
scsupreme={{South Carolina Supreme Court}{S.C.}},
sdsupreme={{South Dakota Supreme Court}{S.D.}},
tnappeals={{Tennessee Court of Appeals}{Tn.  App.}},
tncriminalappeals={{Tennessee Court of Criminal Appeals}{Tn.  Crim. App.}},
tnsupreme={{Tennessee Supreme Court}{Tn.}},
txappeals={{Texas Court of Appeals}{Tx.  App.}},
txcivilappeals={{Texas Court of Civil Appeals}{Tx.  Civ. App.}},
txcriminalappeals={{Texas Court of Criminal Appeals}{Tx.  Crim. App.}},
txsupreme={{Texas Supreme Court}{Tx.}},
utappeals={{Utah Court of Appeals}{Ut.  App.}},
utsupreme={{Utah Supreme Court}{Ut.}},
vtsupreme={{Vermont Supreme Court}{Vt.}},
vaappeals={{Virginia Court of Appeals}{Va.  App.}},
vasupreme={{Virginia Supreme Court}{Va.}},
waappeals={{Washington Court of Appeals}{Wa.  App.}},
wasupreme={{Washington Supreme Court}{Wa.}},
wvsupremeappeals={{West Virginia Supreme Court of Appeals}{W.V.}},
wiappeals={{Wisconsin Court of Appeals}{Wi.  App.}},
wisupreme={{Wisconsin Supreme Court}{Wi.}},
wysupreme={{Wyoming Supreme Court}{Wy. Supreme Court}},
wyfederals={{Wyoming Federal courts}{Wy. Federal courts}},
1stcir={{1st Circuit Court of Appeals}{1st Cir.}},
dme={{1st Circuit D. Maine}{D. Me.}},
dma={{1st Circuit D. Massachusetts}{D. Ma.}},
dnh={{1st Circuit D. New Hampshire}{D. N.H.}},
dpr={{1st Circuit D. Puerto Rico}{D. P.R.}},
dri={{1st Circuit D. Rhode Island}{D. R.I.}},
1stcirbankruptcy={{1st Circuit Bankruptcy Courts}{1st Cir. Bkry.}},
1stcirbankruptcyappellate={{1st Circuit Bankruptcy Appellate Panel}{1st Cir. Bkry. Appl.}},
2ndcir={{2nd Circuit Court of Appeals}{2nd Cir.}},
dct={{2nd Circuit D. Connecticut}{D. Ct.}},
dvt={{2nd Circuit D. Vermont}{D. Vt.}},
edny={{2nd Circuit ED New York}{E.D. N.Y.}},
ndny={{2nd Circuit ND New York}{N.D. N.Y.}},
sdny={{2nd Circuit SD New York}{S.D. N.Y.}},
wdny={{2nd Circuit WD New York}{W.D. N.Y.}},
2ndcirbankruptcy={{2nd Circuit Bankruptcy Courts}{2nd Cir. Bkry.}},
2ndcirbankruptcyappellate={{2nd Circuit Bankruptcy Appellate Panel}{2nd Cir. Bkry. Appl.}},
3rdcir={{3rd Circuit Court of Appeals}{3rd Cir.}},
dde={{3rd Circuit D. Delaware}{D. De.}},
dnj={{3rd Circuit D. New Jersey}{D. N.J.}},
dvi={{3rd Circuit D. Virgin Islands}{D. V.I.}},
edpa={{3rd Circuit ED Pennsylvania}{E.D. Pa.}},
mdpa={{3rd Circuit MD Pennsylvania}{M.D. Pa.}},
wdpa={{3rd Circuit WD Pennsylvania}{W.D. Pa.}},
3rdcirbankruptcy={{3rd Circuit Bankruptcy Courts}{3rd Cir. Bkry.}},
4thcir={{4th Circuit Court of Appeals}{4th Cir.}},
dmd={{4th Circuit D. Maryland}{D. Md.}},
dsc={{4th Circuit D. South Carolina}{D. S.C.}},
ednc={{4th Circuit ED North Carolina}{E.D. N.C.}},
mdnc={{4th Circuit MD North Carolina}{M.D. N.C.}},
wdnc={{4th Circuit WD North Carolina}{W.D. N.C.}},
edva={{4th Circuit ED Virginia}{E.D. Va.}},
wdva={{4th Circuit WD Virginia}{W.D. Va.}},
ndwv={{4th Circuit ND West Virginia}{N.D. W.V.}},
sdwv={{4th Circuit SD West Virginia}{S.D. W.V.}},
4thcirbankruptcy={{4th Circuit Bankruptcy Courts}{4th Cir. Bkry.}},
5thcir={{5th Circuit Court of Appeals}{5th Cir.}},
edla={{5th Circuit ED Louisiana}{E.D. La.}},
mdla={{5th Circuit MD Louisiana}{M.D. La.}},
wdla={{5th Circuit WD Louisiana}{W.D. La.}},
ndms={{5th Circuit ND Mississippi}{N.D. Ms.}},
sdms={{5th Circuit SD Mississippi}{S.D. Ms.}},
edtx={{5th Circuit ED Texas}{E.D. Tx.}},
ndtx={{5th Circuit ND Texas}{N.D. Tx.}},
sdtx={{5th Circuit SD Texas}{S.D. Tx.}},
wdtx={{5th Circuit WD Texas}{W.D. Tx.}},
5thcirbankruptcy={{5th Circuit Bankruptcy Courts}{5th Cir. Bkry.}},
6thcir={{6th Circuit Court of Appeals}{6th Cir.}},
edky={{6th Circuit ED Kentucky}{E.D. Ky.}},
wdky={{6th Circuit WD Kentucky}{W.D. Ky.}},
edmi={{6th Circuit ED Michigan}{E.D. Mi.}},
wdmi={{6th Circuit WD Michigan}{W.D. Mi.}},
ndoh={{6th Circuit ND Ohio}{N.D. Oh.}},
sdoh={{6th Circuit SD Ohio}{S.D. Oh.}},
edtn={{6th Circuit ED Tennessee}{E.D. Tn.}},
mdtn={{6th Circuit MD Tennessee}{M.D. Tn.}},
wdtn={{6th Circuit WD Tennessee}{W.D. Tn.}},
6thcirbankruptcy={{6th Circuit Bankruptcy Courts}{6th Cir. Bkry.}},
6thcirbankruptcyappellate={{6th Circuit Bankruptcy Appellate Panel}{6th Cir. Bkry. Appl.}},
7thcir={{7th Circuit Court of Appeals}{7th Cir.}},
cdil={{7th Circuit CD Illinois}{C.D. Il.}},
ndil={{7th Circuit ND Illinois}{N.D. Il.}},
sdil={{7th Circuit SD Illinois}{S.D. Il.}},
ndin={{7th Circuit ND Indiana}{N.D. In.}},
sdin={{7th Circuit SD Indiana}{S.D. In.}},
edwi={{7th Circuit ED Wisconsin}{E.D. Wi.}},
wdwi={{7th Circuit WD Wisconsin}{W.D. Wi.}},
7thcirbankruptcy={{7th Circuit Bankruptcy Courts}{7th Cir. Bkry.}},
8thcir={{8th Circuit Court of Appeals}{8th Cir.}},
8thcirminnesota={{8th Circuit Minnesota}{8th Cir. Bkry.}},
dne={{8th Circuit D. Nebraska}{D. Ne.}},
dnd={{8th Circuit D. North Dakota}{D. N.D.}},
dsd={{8th Circuit D. South Dakota}{D. S.D.}},
edar={{8th Circuit ED Arkansas}{E.D. Ar.}},
wdar={{8th Circuit WD Arkansas}{W.D. Ar.}},
ndia={{8th Circuit ND Iowa}{N.D. Ia.}},
sdia={{8th Circuit SD Iowa}{S.D. Ia.}},
edmo={{8th Circuit ED Missouri}{E.D. Mo.}},
wdmo={{8th Circuit WD Missouri}{W.D. Mo.}},
8thcirbankruptcy={{8th Circuit Bankruptcy Courts}{8th Cir. Bkry.}},
8thcirbankruptcyappellate={{8th Circuit Bankruptcy Appellate Panel}{8th Cir. Bkry. Appl.}},
9thcir={{9th Circuit Court of Appeals}{9th Cir.}},
dak={{9th Circuit D. Alaska}{D. Ak.}},
daz={{9th Circuit D. Arizona}{D. Az.}},
dgu={{9th Circuit D. Guam}{D. Gu.}},
dhi={{9th Circuit D. Hawaii}{D. Hi.}},
did={{9th Circuit D. Idaho}{D. Id.}},
dmt={{9th Circuit D. Montana}{D. Mt.}},
dnv={{9th Circuit D. Nevada}{D. Nv.}},
dor={{9th Circuit D. Oregon}{D. Or.}},
cdca={{9th Circuit CD California}{C.D. Ca.}},
edca={{9th Circuit ED California}{E.D. Ca.}},
ndca={{9th Circuit ND California}{N.D. Ca.}},
sdca={{9th Circuit SD California}{S.D. Ca.}},
edwa={{9th Circuit ED Washington}{E.D. Wa.}},
wdwa={{9th Circuit WD Washington}{W.D. Wa.}},
9thcirbankruptcy={{9th Circuit Bankruptcy Courts}{9th Cir. Bkry.}},
9thcirbankruptcyappellate={{9th Circuit Bankruptcy Appellate Panel}{9th Cir. Bkry. Appl.}},
10thcir={{10th Circuit Court of Appeals}{10th Cir.}},
dco={{10th Circuit D. Colorado}{D. Co.}},
dks={{10th Circuit D. Kansas}{D. Ks.}},
dnm={{10th Circuit D. New Mexico}{D. N.M.}},
dut={{10th Circuit D. Utah}{D. Ut.}},
dwy={{10th Circuit D. Wyoming}{D. Wy.}},
edok={{10th Circuit ED Oklahoma}{E.D. Ok.}},
ndok={{10th Circuit ND Oklahoma}{N.D. Ok.}},
wdok={{10th Circuit WD Oklahoma}{W.D. Ok.}},
10thcirbankruptcy={{10th Circuit Bankruptcy Courts}{10th Cir. Bkry.}},
10thcirbankruptcyappellate={{10th Circuit Bankruptcy Appellate Panel}{10th Cir. Bkry. Appl.}},
11thcir={{11th Circuit Court of Appeals}{11th Cir.}},
mdal={{11th Circuit MD Alabama}{M.D. Al.}},
ndal={{11th Circuit ND Alabama}{N.D. Al.}},
sdal={{11th Circuit SD Alabama}{S.D. Al.}},
mdfl={{11th Circuit MD Florida}{M.D. Fl.}},
ndfl={{11th Circuit ND Florida}{N.D. Fl.}},
sdfl={{11th Circuit SD Florida}{S.D. Fl.}},
mdga={{11th Circuit MD Georgia}{M.D. Ga.}},
ndga={{11th Circuit ND Georgia}{N.D. Ga.}},
sdga={{11th Circuit SD Georgia}{S.D. Ga.}},
11thcirbankruptcy={{11th Circuit Bankruptcy Courts}{11th Cir. Bkry.}},
dccir={{D.C. Circuit Court of Appeals}{d.c. Cir.}},
dccirdc={{D.C. Circuit Dist. of Columbia}{d.c. Cir. Bkry.}},
dccirbankruptcy={{D.C. Circuit Bankruptcy Courts}{d.c. Cir. Bkry.}}
}
